Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-30 PAPER.tex
added back in that the peak of p_x is from the no-bootstrapping case

We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process, and we smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function. Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.

>>>>

We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case. We smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function. Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
